---
title: "Image Wall Trial"
output: html_document
date: "2024-07-25"
---

# Load Data

```{r}
library(tidyverse)
```

First let's get a sample of some permalinks to embed

```{r}
data <- ParseR::sprinklr_export %>% janitor::clean_names()
data %>% colnames()
data %>% distinct(social_network)

data %>% pull(permalink) %>% extract_source() %>% unique()

permalink_samp <- data %>%
  group_by(social_network) %>%
  sample_n(5) %>%
  ungroup() %>%
  pull(permalink)

linkedin_permalinks <- c(
  "https://www.linkedin.com/feed/update/urn:li:share:7188476727067594753",
  "https://www.linkedin.com/feed/update/urn:li:ugcPost:7208453444964134912",
  "https://www.linkedin.com/feed/update/urn:li:ugcPost:7185940056908476416",
  "https://www.linkedin.com/feed/update/urn:li:ugcPost:7194275003356381184",
  "https://www.linkedin.com/feed/update/urn:li:ugcPost:7183750606958776320",
  "https://www.linkedin.com/feed/update/urn:li:ugcPost:7202308920336351232")

youtube_samp <- c("https://www.youtube.com/shorts/sqVTJZ_Fkq0",
                  "https://www.youtube.com/shorts/FgU8s99P_zk",
                  "https://www.youtube.com/watch?v=vIvxoy9jQn8",
                  "https://www.youtube.com/shorts/QRNVpT0mg_Q",
                  "https://www.youtube.com/shorts/rIk6KDFuiCw")

facebook_permalinks <- c(
  "https://www.facebook.com/photo.php?fbid=764788502502938&set=a.560181062963684&type=3",
  "https://www.facebook.com/560181189630338/posts/755938223387966",
  "https://www.facebook.com/560181189630338/posts/759706999677755",
  "https://www.facebook.com/photo.php?fbid=751491823832606&set=a.560181062963684&type=3",
  "https://www.facebook.com/560181189630338/posts/735957828719339",
  "https://www.facebook.com/560181189630338/videos/26002920519322208")

threads_permalinks <- c(
  "https://www.threads.net/@gulfoilinternational/post/C5Vy-exOMrT",
  "https://www.threads.net/@gulfoilinternational/post/C6YvYULovce",
  "https://www.threads.net/@gulfoilinternational/post/C6qxNOauTze",
  "https://www.threads.net/@gulfoilinternational/post/C7OZBQsNbvQ",
  "https://www.threads.net/@gulfoilinternational/post/C66Zv81t8vf")

tiktok_permalinks <- c(
  "https://www.tiktok.com/@gulfoilinternational/video/7353995974261493025",
  "https://www.tiktok.com/@gulfoilinternational/video/7242299307963976965",
  "https://www.tiktok.com/@gulfoilinternational/video/7240412922386648326",
  "https://www.tiktok.com/@gulfoilinternational/video/7247834632450772229",
  "https://www.tiktok.com/@gulfoilinternational/video/7310225736944700704")

```


# Functions for embedding

Ok now we have some permalinks - let's render them, this is the code from the demoApp:

General functions:
```{r}
extract_source <- function(permalink) stringr::str_extract(permalink, "(\\w+)\\.(com|net|co\\.uk)", group = 1)

embed_switch <- function(permalink) {
  source <- extract_source(permalink)
  
  embed <- switch(
    source,
    "reddit" = create_reddit_embed(permalink),
    "instagram" = create_instagram_embed(permalink),
    "x" = create_tweet_embed(permalink),
    "youtube" = create_youtube_embed(permalink),
    "facebook" = create_facebook_embed(permalink),
    "linkedin" = create_linkedin_embed(permalink),
    "threads" = create_threads_embed(permalink),
    "tiktok" = create_tiktok_embed(permalink)
  )

  return(embed )
}

# sets the max height and makes element scrollable
style_embedding <- function(height = 717) {
                            # width = 403) {
  start_div <- paste0("<div style='height: ", height, "px; overflow-y: auto;'>")
                      # width: ", width, "px; 
  end_div <- "</div>"
  
  return(list(start_div = start_div, end_div = end_div))
}

style_embedding_expand <- function(height = 717){
  
   start_div <- paste0("<div style='height: ", height, "px; overflow-y: auto; position: relative; width: 100%; padding-bottom: 200%; height: 0; overflow: hidden; max-width: 100%; background: #fff;'>")
                      # width: ", width, "px; 
  end_div <- "</div>"
  
  return(list(start_div = start_div, end_div = end_div))
}
```

Embed Reddits
```{r}
create_reddit_embed <- function(permalink){
  if(!grepl("reddit", permalink)) stop("Not a reddit link")
  
  subreddit <- extract_subreddit(permalink)
  
  reddit_html <- extract_reddit_html(permalink, subreddit)
  
  return(reddit_html)
}

extract_subreddit <- function(permalink) stringr::str_extract(permalink, "/r/(\\w+)", group = 1)

extract_reddit_html <- function(url, subreddit) {
  
  embedding_style <- style_embedding(height = 500)
  html <- paste0(embedding_style$start_div, '<blockquote class="reddit-embed-bq" style="height:400px" data-embed-height="597"><a href="',
                 url, '">Link to post</a><br></a> in<a href="https://www.reddit.com/r/', subreddit, '">',
                 subreddit, '</a></blockquote><script async="" src="https://embed.reddit.com/widgets.js" charset="UTF-8"></script>',
                 embedding_style$end_div)
  
  return(shiny::HTML(html))
}
```

Embed Instagram
```{r}
create_instagram_embed <- function(permalink) {
    
    embedding_style <- style_embedding(height = 717)
    
    html <- paste0(embedding_style$start_div,'<blockquote class="instagram-media" data-instgrm-permalink="',
                   permalink, '" data-instgrm-version="12" style=" background:#FFF; border:0; border-radius:3px; box-shadow:0 0 1px 0 rgba(0,0,0,0.5),0 1px 10px 0 rgba(0,0,0,0.1); margin: 1px; max-width:540px; min-width:326px; padding:0; width:99.375%; width:-webkit-calc(100% - 2px); width:calc(100% - 2px);">
      <div style="padding:16px;">
      </div>
    </blockquote>
    <script async defer src="//www.instagram.com/embed.js"></script>', embedding_style$end_div)
    
    return(shiny::HTML(html))
}
```

Embed Tweets - this needs some work
```{r}
create_tweet_embed <- function(permalink) {
  tweet_id <- extract_tweet_id(permalink)
  tweet_screen_name <- extract_tweet_screen_name(permalink)
  embedding_style <- style_embedding(height = 500)
  
  tweet_blockquote <- get_tweet_blockquote(screen_name = tweet_screen_name, status_id = tweet_id)
  
  # x_logo <-  shiny::tags$img(src ="x_logo.png", align = "left",
  #                            width = "36px", height = "30px",
  #                            style = "margin-left: 20px; margin-right: 10px")

  x_logo <-  htmltools::tags$img(src ="x_logo.png", align = "right",
                             width = "36px", height = "30px",
                             style = "margin-right: 20px; margin-bottom: 50px")
 
  if (!is.null(tweet_blockquote)) {
    html <- paste0(
      embedding_style$start_div,
      tweet_blockquote, 
      x_logo,
      embedding_style$end_div)
    
    return(shiny::HTML(html))
  } else {
    
    return(NULL)
  }
}

extract_tweet_id <- function(permalink) stringr::str_extract(permalink, "status/(\\d+)", group = 1)

extract_tweet_screen_name <- function(permalink){
  
  if (length(grep("x.com", permalink))){
    stringr::str_extract(permalink, "x.com/(\\w+)", group = 1)
  } else {
    stringr::str_extract(permalink, "twitter.com/(\\w+)", group = 1)
  }
} 

# Yoinked from Gadenbuie's Tweet Conf package
get_tweet_blockquote <- function(screen_name, status_id, ..., null_on_error = TRUE, theme = "light") {
  oembed <- list(...)$oembed
  if (!is.null(oembed) && !is.na(oembed)) return(unlist(oembed))
  # oembed_url <- glue::glue("https://publish.twitter.com/oembed?url=https://twitter.com/{screen_name}/status/{status_id}&omit_script=1&dnt=1&theme={theme}")
  oembed_url <- glue::glue("https://publish.twitter.com/oembed?url=https://twitter.com/{screen_name}/status/{status_id}&omit_script=1&dnt=1&theme={theme}")
  bq <- purrr::possibly(httr::GET, list(status_code = 999))(URLencode(oembed_url))
  if (bq$status_code >= 400) {
    if (null_on_error) return(NULL)
    '<blockquote style="font-size: 90%">Sorry, unable to get tweet ¯\\_(ツ)_/¯</blockquote>'
  } else {
    httr::content(bq, "parsed")$html
  }
}

# this is plucked from gadenbuie's tweetrmd file
tweet_blockquote <- function(
  tweet_url,
  maxwidth = 550,
  hide_media = FALSE,
  hide_thread = FALSE,
  omit_script = TRUE,
  align = c("none", "left", "right", "center"),
  related = NULL,
  lang = "en",
  theme = c("light", "dark"),
  link_color = NULL,
  widget_type = NULL,
  dnt = TRUE,
  ...,
  result_only = FALSE
) {
  align <- match.arg(align)
  theme <- match.arg(theme)
  if (!is.null(widget_type) && !identical(widget_type, "video")) {
    stop("`widget_type` must be NULL or 'video'")
  }

  url <- httr::parse_url("https://publish.twitter.com/oembed")
  url$query <- list(
    url = tweet_url,
    maxwidth = maxwidth,
    hide_media = validate_true(hide_media),
    hide_thread = validate_true(hide_thread),
    omit_script = omit_script,
    align = align,
    related = related %||% paste(related, collapse = ","),
    lang = lang,
    theme = theme,
    link_color = link_color,
    widget_type = widget_type,
    dnt = validate_true(dnt),
    ...
  )

  url <- httr::build_url(url)
  res <- httr::GET(url)
  httr::stop_for_status(res)
  if (!grepl("application/json", res$headers$`content-type`)) {
    stop("Expected json response, got ", res$headers$`content-type`)
  }
  if (isTRUE(result_only)) return(res)
  res_txt <- httr::content(res, "text")
  res_json <- jsonlite::fromJSON(res_txt)
  htmltools::HTML(res_json$html)
}

validate_true <- function(x) {
  if (isTRUE(x) || identical(tolower(x), "t") || x == 1) {
    TRUE
  } else FALSE
}

tweet_embed <- function(
  tweet_url,
  maxwidth = 550,
  plain = FALSE,
  hide_media = FALSE,
  hide_thread = FALSE,
  omit_script = TRUE,
  align = c("none", "left", "right", "center"),
  related = NULL,
  lang = "en",
  theme = c("light", "dark"),
  link_color = NULL,
  widget_type = NULL,
  dnt = TRUE
) {

  if (plain) omit_script <- TRUE

  bq <- tweet_blockquote(
    tweet_url   = tweet_url,
    maxwidth    = maxwidth,
    hide_media  = hide_media,
    hide_thread = hide_thread,
    omit_script = omit_script,
    align       = align,
    related     = related,
    lang        = lang,
    theme       = theme,
    link_color  = link_color,
    widget_type = widget_type,
    dnt         = dnt
  )

  if (omit_script & !plain) {
    bq <- htmltools::tagList(html_dependency_twitter(), bq)
  }
  htmltools::browsable(bq)
}

html_dependency_twitter <- function() {
  htmltools::htmlDependency(
    name = "twitter-widget",
    version = "0.0.1",
    package = "tweetrmd",
    src = c(
      file = "tw",
      href = "https://platform.twitter.com/"
    ),
    script = "widgets.js",
    all_files = FALSE
  )
}

```

Try something new
```{r}
# install.packages("devtools")
devtools::install_github("gadenbuie/tweetrmd")

test <- tweetrmd::tweet_embed(permalink_samp[[6]])
tweetrmd::tweet_screenshot(permalink_samp[[6]])
class(test)

print(test)
```

From here are functions that I have made for new sources

YouTube - I have removed the standard styling so I might need to go back and look at this
```{r}

# '<iframe width="560" height="315" src="https://www.youtube.com/embed/vIvxoy9jQn8?si=EP1VYvTPxHTg96te" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" referrerpolicy="strict-origin-when-cross-origin" allowfullscreen></iframe>'

# '<iframe width="403" height="717" src="https://www.youtube.com/embed/sqVTJZ_Fkq0" title="Unstoppable Journeys" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" referrerpolicy="strict-origin-when-cross-origin" allowfullscreen></iframe>'

create_youtube_embed <- function(permalink) {

    if (length(grep("short", permalink)) > 0){
    width <- 403
    height <- 717
    permalink_split <- strsplit(permalink, "shorts", fixed = TRUE)[[1]]
  } else{
    width <- 560
    height <- 315
    permalink_split <- strsplit(permalink, "watch?v=", fixed = TRUE)[[1]]
    permalink_split[2] <- paste0("/", permalink_split[2])
  }
    
    html <- paste0(
      '<iframe width="', width, '" height="', height, '" src="', permalink_split[1], 'embed', permalink_split[2], '" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" referrerpolicy="strict-origin-when-cross-origin" allowfullscreen></iframe>'
      )
    
    return(shiny::HTML(html))
}
```

Facebook - I can't change height ratio but I can make it all have a max height - maybe I could look more into iframe?
```{r}
create_facebook_embed <- function(permalink) {
    width <- 403
    height <- 717
    embedding_style <- style_embedding(height = 717)
    
    if(length(grep("video", permalink)) > 0){
      class <- "video"
    } else {
      class <- "post"
    }
    print(class)
    
    html <- paste0(
      # embedding_style$start_div,
    '<div id="fb-root"></div>
<script async defer src="https://connect.facebook.net/en_US/sdk.js#xfbml=1&version=v3.2"></script>',
'<div class="fb-', class, '" data-href="', permalink, '"  data-width="', 
width,
# "auto",
'" data-show-text="true" style="border:none;overflow:hidden;height:717px; scrolling="no" frameborder="0" allowfullscreen="true" allow="autoplay"></div>'
# embedding_style$end_div
)
    
    return(shiny::HTML(html))
}

```

Linkedin
```{r}
create_linkedin_embed <- function(permalink){
  split_perm <- strsplit(permalink, "feed", fixed = T)
  
  width <- "403"
  height <- "717"
  
  html <- paste0('<div class="embed-container"><iframe src="', split_perm[[1]][1], 'embed/feed', split_perm[[1]][2],
         '" height="', height, '" width="', width, '" frameborder="0" allowfullscreen="" title="Embedded post"></iframe></div>')
  
  return(shiny::HTML(html))
}
```

Threads
```{r}
create_threads_embed <- function(permalink){
  width <- 403
  height <- 717
  
  # embedding_style <- style_embedding_expand(height = 717)
  # embedding_style <- style_embedding(height = 717)
  
  html <- paste0(
    # embedding_style$start_div,
    # '<div class="threads-post">',
    '<iframe src="', permalink, '/embed" width="', width, '" height="', height, '" frameborder="0" style="border:none;overflow:hidden" scrolling="no" frameborder="0" allowTransparency="true" allowFullScreen="true"></iframe>',
    # embedding_style$end_div,
    embedding_style$end_div)
  
  return(shiny::HTML(html))
}


```

tiktok - this is taken from gadenbuie
```{r}
create_tiktok_embed <- function(url) {
  tt_oembed_url <- sprintf(
    "https://www.tiktok.com/oembed?url=%s",
    eg
  )
  res <- httr::GET(tt_oembed_url)
  httr::stop_for_status(res, "Get embedding information from tiktok")
  tt <- httr::content(res)

  expected_items <- c("title", "author_name", "author_url", "html")
  if (!all(expected_items %in% names(tt))) {
    warning(
      "Received unusual response from TikTok oEmbed API ",
      "for this video:", url,
      immediate. = TRUE
    )
  }

  return(shiny::HTML(tt$html))
}

```

```{r}
remotes::install_github("gadenbuie/tiktokrmd")
library(tiktokrmd)

tt_url <- "https://www.tiktok.com/@aquickspoonful/video/6890681375431691526"
tt <- tiktok_embed(tt_url)

## # in R Markdown, just print the object to embed it
## tt

# Or write a plain markdown version
tiktok_md(tt)
#> [1] "![[#cake #cakes #dontmixit #cakelover #cakelovers #dumpcake #food #tiktokfood #foodtiktok #easyrecipe #easyrecipes #peach #peaches #cinnamon #fyp](https://www.tiktok.com/@aquickspoonful/video/6890681375431691526) by [Sophia Wasu](https://www.tiktok.com/@aquickspoonful)](https://p16-sign-va.tiktokcdn.com/obj/tos-maliva-p-0068/00189a8b703343bd817a3ccaec240f71?x-expires=1610654400&x-signature=ExJZaEMAgxhyXydfgsqgZqU%2B8y8%3D)"

# Or as HTML without the full TikTok embedded player shenanigans
tiktok_html(tt, include_player = FALSE)
```

# Embed

embed docs
```{r}
embedded_posts <- lapply(c(permalink_samp, youtube_samp, facebook_permalinks, linkedin_permalinks, threads_permalinks), embed_switch)
```

display in shiny app
```{r}
library(shiny)

ui <- fluidPage(
    # tags$head(
    # tags$style(HTML("
    #   .embed-container {
    #     position: relative;
    #     width: 100%;
    #     padding-bottom: 20%; /* This maintains a 16:9 aspect ratio */
    #     height: 0;
    #     overflow: hidden;
    #     max-width: 100%;
    #     background: #000;
    #   }
    #   .fb-post, .fb-video {
    #     position: absolute;
    #     top: 0;
    #     left: 0;
    #     width: 100%;
    #     height: 100%;
    #   } 
    # ")) # this is what makes the fb posts a constant max height - ok idk is this actually working - look more at later
  # ),
  uiOutput("renders")
)

server <- function(input, output) {
  output$renders <- renderUI({
    do.call(bslib::layout_column_wrap, c(width = 1/3, embedded_posts))
  })
}

shiny::shinyApp(ui, server)
```

- Twitter posts not rendering at all
- 4th reddit post says "Not supported comment"
- First instagram post renders but says "link may be broken"
```{r}
permalink_samp[[14]] # "Not supported comment" reddit post - banned user
embedded_posts[[14]] 

embedded_posts[[6]]
```

The twitter function is returning a "NULL" value and there is nothing in the reddit embedded post that indicates that the account is banned so not sure how we could safeguard against that.

Let's look at Twitter a bit closer. For this permalink
```{r}
'https://www.twitter.com/PS44ShineOn/status/1053293768999387136'
```

This is the embedded post
```{r}
test_x <- '<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Celebrating Hispanic Heritage Month <a href="https://twitter.com/hashtag/alightintheharbor?src=hash&amp;ref_src=twsrc%5Etfw">#alightintheharbor</a> <a href="https://twitter.com/hashtag/inspired31?src=hash&amp;ref_src=twsrc%5Etfw">#inspired31</a> <a href="https://t.co/tr5ohyfAfC">pic.twitter.com/tr5ohyfAfC</a></p>&mdash; PS44 (@PS44ShineOn) <a href="https://twitter.com/PS44ShineOn/status/1053293768999387136?ref_src=twsrc%5Etfw">October 19, 2018</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>'


ui <- fluidPage(
  shiny::HTML(test_x)
)

server <- function(input, output, session) {
}

shiny::shinyApp(ui, server)
```

I stole this function from gadenbuie's website
```{r}
get_tweet_blockquote <- function(screen_name, status_id, ..., null_on_error = TRUE, theme = "light") {
  oembed <- list(...)$oembed
  if (!is.null(oembed) && !is.na(oembed)) return(unlist(oembed))
  oembed_url <- glue::glue("https://publish.twitter.com/oembed?url=https://twitter.com/{screen_name}/status/{status_id}&omit_script=1&dnt=1&theme={theme}")
  bq <- possibly(httr::GET, list(status_code = 999))(URLencode(oembed_url))
  if (bq$status_code >= 400) {
    if (null_on_error) return(NULL)
    '<blockquote style="font-size: 90%">Sorry, unable to get tweet ¯\\_(ツ)_/¯</blockquote>'
  } else {
    httr::content(bq, "parsed")$html
  }
}

test_gen_permalink <- get_tweet_blockquote(screen_name = "PS44ShineOn",
                     status_id = 1053293768999387136)

ui <- fluidPage(
  shiny::HTML(test)
)

server <- function(input, output, session) {
}

shiny::shinyApp(ui, server)
```

What about youtube?
```{r}

embedded_youtube <- lapply(youtube_samp, embed_switch)

library(shiny)

ui <- fluidPage(
  uiOutput("renders")
)

server <- function(input, output) {
  output$renders <- renderUI({
    do.call(bslib::layout_column_wrap, c(width = 1/3, c(embedded_youtube, embedded_posts[-c(6:10)])))
  })
}

shiny::shinyApp(ui, server)
```

What about an instagram video

```{r}
reel_embed <- embed_switch("https://www.instagram.com/reel/C841d2QoesC/")

ui <- fluidPage(
  shiny::HTML(reel_embed)
)

server <- function(input, output, session) {
}

shiny::shinyApp(ui, server)
```

This works!!

```{r}
embedded_tweet <- tweet_blockquote(permalink_samp[[6]])

ui <- fluidPage(
  # shiny::HTML(tweet_blockquote)
  shiny::uiOutput("testing_twitter")
)

server <- function(input, output, session) {
  output$testing_twitter <- renderUI({
     # htmltools::browsable(htmltools::tagList(html_dependency_twitter(), embedded_tweet))
    permalink_samp[6:9] %>%
      pmap_chr(get_tweet_blockquote) %>%
        HTML()
  })
}

shiny::shinyApp(ui, server)
```
